target_offtarget

### 2025-01-22 manuscript_figures.Rmd
Figure S4 update

## Not required ?Figure S4

@@

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_respiratory_syncytial_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("log10(Coverage)") +
  ggtitle("Human RSV (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))
```

#### ***Final plot***
```{r}
#ggsave("figures/manuscript_figures_pdf/FigureS5.pdf",width=10,height=8)
```

>>>>

## No longer required? Figure S4

@@

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_respiratory_syncytial_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Human RSV (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))
```

#### ***Final plot***
```{r}
ggsave("figures/manuscript_figure_2025/PDF/Figure_S4.pdf",
       width=9,
       height=8)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S4.png",
       width=9,
       height=8)
```
